Linear variation and an optimization of algorithms for connected components labeling in a binary image

### 2016-02-06 paper/paper.tex
Add condensation types subsubsubsection

This modification of SUF was taken to compare the optimization we present with
another optimization suggested by Wu, Otoo and Suzuki, % TODO reference
namely decision tree.
Unfortunately DTSUF (Decision Tree Scan plus Union-Find) is not
applicable for condensed image, as it exploits similar observations on 8-connectivity.

@@

bla-bla about 2x2 in memory and as a view

\newcommand{\inputtable}[2]{
  \begin{table}[p]
    \centering
    \input{../bench-out/#1x#2}
    \caption{Noise images $#1 \times #2$ px}
    \label{tab:noise#1x#2}
  \end{table} }

>>>>

This modification of SUF was implemented to compare the optimization we present with
another optimization suggested by Wu, Otoo and Suzuki, % TODO reference
namely decision tree.
Unfortunately DTSUF (Decision Tree Scan plus Union-Find) is not
applicable for condensed image, as it exploits similar observations on 8-connectivity.

@@

For memory-tight applications such as embedded systems it can be useful to
utilise the suggested condensation in a lazy way, so that without actually
constructing the condensed image we use a function (``view'') calculating color of
each cell with 4 lookups to the original binary image.
This is probably most interesting combined with SUF2 algorithm, as it is a way
to win some time without increasing memory footprint.
However this lazy approach increases the number of image lookups.
So, according to our benchmark, this combination is efficient only for dense
($>30\%$) noise.

So the benchmark tables show three levels of optimization applied to
DFS, SUF and SUF2:
``no'' meaning no condensation, ``view'' meaning lazy memory-less condensation
and ``yes'' meaning that a temporary condensed image was constructed in memory.
For the latter case, the construction time was included into the overall measured
time of run.

\subsection{Results}

some results

\section{Summary and future work}

\newcommand{\inputtable}[2]{
  \begin{table}[p]
    \centering
    \input{../bench-out/#1x#2}
    \caption{Average milliseconds of cpu time per run on noise images $#1 \times #2$ px}
    \label{tab:noise#1x#2}
  \end{table} }
